A Two-Infall Star Formation History with Outflows and Radial Migration

### 2025-01-31 src/tex/ms.tex

\begin{figure*}
    \centering
    \includegraphics{src/tex/figures/ofe_df_comparison.pdf}
    \caption{Stellar [O/Fe] distributions produced by multi-zone models (a--d) and as observed by APOGEE (d). Stars are binned by Galactocentric radius, represented by the color scale, and absolute midplane distance $|z|$, represented by the different rows. Each distribution is normalized so that the area under the curve is 1, and the vertical scale is consistent across each row. The median APOGEE abundance uncertainties were forward-modeled onto the model outputs. For visual clarity, each distribution is smoothed with a box-car of width 0.05 dex. Model (a) assumes the fiducial parameters and the {\tt yZ1} yield set, whereas models (b--d) assume the {\tt yZ2} yield set. Model (c) also assumes a power-law SN Ia DTD, while model (d) assumes the infalling gas has metallicity ${\rm [O/H]}_{\rm CGM}={\rm [Fe/H]}_{\rm CGM}=-0.7$. The distributions from APOGEE DR17 are plotted in column (e) for reference. {\bf Key takeaway:} The high-yield case produces a peak at intermediate [O/Fe] which is prominent in most galactic regions, which can be mitigated by pre-enriched infall.}
    \label{fig:ofe-df-yields}
\end{figure*}

>>>>

\begin{figure*}
    \centering
    \includegraphics{src/tex/figures/ofe_df_comparison.pdf}
    \caption{Stellar [O/Fe] distributions produced by multi-zone models (a--d) and as observed by APOGEE (d). Stars are binned by Galactocentric radius, represented by the color scale, and absolute midplane distance $|z|$, represented by the different rows. Each distribution is normalized so that the area under the curve is 1, and the vertical scale is consistent across each row. The median APOGEE abundance uncertainties were forward-modeled onto the model outputs. For visual clarity, each distribution is smoothed with a box-car of width 0.05 dex. Model (a) assumes the fiducial parameters and the {\tt yZ1} yield set, whereas models (b--d) assume the {\tt yZ2} yield set. Model (c) also assumes a power-law SN Ia DTD, while model (d) assumes the infalling gas has metallicity ${\rm [O/H]}_{\rm CGM}={\rm [Fe/H]}_{\rm CGM}=-0.7$. The distributions from APOGEE DR17 are plotted in column (e) for reference. {\bf Key takeaway:} The high-yield case produces a peak at intermediate [O/Fe] which is prominent in most galactic regions, which can be mitigated by pre-enriched infall.}
    \label{fig:ofe-df}
\end{figure*}

As noted by \citet{dubay_galactic_2024} two-infall model generically predicts {\it three} peaks in the [O/Fe] distribution which correspond to the high-$\alpha$ sequence, the abundance ``turn-over'' after the second infall, and finally the late-time low-$\alpha$ sequence. Figure \ref{fig:ofe-df} compares [O/Fe] distributions across the Galactic disk produced by four different multi-zone models with the distributions observed in APOGEE DR17. For the fiducial model (a) with $y/Z_\odot=1$, the latter two peaks are close together and the overall effect is similar to the observed distribution. With a higher yield set, however, there is a $\sim0.2$ dex separation between the low- and intermediate-$\alpha$ peaks, because the CCSN element production after the second infall is more efficient. As a result, model (b) predicts a high density of stars in the APOGEE ``trough.''
